Eye-tracking on the web: lessons learned from replicating 5 experiments

### 2022-04-01 group-d/E4-analysis-calibration.Rmd
minor fix to  manuscript

m_calib = broom::tidy(lm(bias_effect ~ mean_percent_in_roi, data = eyetracking.effects.by.subj))
#m_calib 
```

```{r}
m_calib_b = m_calib %>% filter(term ==  'mean_percent_in_roi') %>% pull(estimate ) %>% round(digits = 3)
m_calib_se = m_calib %>% filter(term ==  'mean_percent_in_roi') %>% pull(std.error ) %>% round(digits = 3)
m_calib_p = m_calib %>% filter(term ==  'mean_percent_in_roi') %>% pull(p.value ) %>% round(digits = 3)
```

```{r, eval = F}
ggplot(eyetracking.effects.by.subj, aes(x = mean_percent_in_roi, y = bias_effect))+
  geom_point()+
  geom_smooth(method = "lm")
```
Participants' calibration quality, measured as the mean percentage of fixations that landed within XX pixels of the calibration point, varied substantially (`r range(calib.by.subj$mean_percent_in_roi) |> round(digits = 2)`). 
The quality of a participant's calibration significantly predicted the participant's effect size. 
The difference in target animal fixation proportions between modifier and instrument conditions was higher for participants with better calibration ($b=$`r m_calib_b`,$SE=$`r m_calib_se`, $p=$`r m_calib_p`).

>>>>

m_calib = broom::tidy(cor.test(eyetracking.effects.by.subj$mean_percent_in_roi, eyetracking.effects.by.subj$bias_effect))
#m_calib 
```

```{r}
m_calib_r = m_calib %>% pull(estimate )

```{r, eval = F}
ggplot(eyetracking.effects.by.subj, aes(x = mean_percent_in_roi, y = bias_effect))+
  geom_point()+
  geom_smooth(method = "lm")
```
Participants' calibration quality, measured as the mean percentage of fixations that landed within `r colorize("XX", "red")` pixels of the calibration point, varied substantially (between `r range(calib.by.subj$mean_percent_in_roi) |> round(digits = 2)` %). 
The quality of a participant's calibration significantly correlated with the participant's effect size ( _Pearson's r_= `r m_calib_r`, _p_ < 0.05).
The difference in target animal fixation proportions between modifier and instrument conditions was higher for participants with better calibration

### 2022-04-01 manuscript.tex
minor fix to  manuscript

Participants' calibration quality, measured as the mean percentage of fixations that landed within XX pixels of the calibration point, varied substantially (2.22 and 97.36).
The quality of a participant's calibration significantly predicted the participant's effect size.
The difference in target animal fixation proportions between modifier and instrument conditions was higher for participants with better calibration (\$b=\(0.00,\)SE=\$0.00, \$p=\$0.03).

>>>>

Participants' calibration quality, measured as the mean percentage of fixations that landed within \textcolor{red}{XX} pixels of the calibration point, varied substantially (between 2.22 and 97.36 \%).
The quality of a participant's calibration significantly correlated with the participant's effect size ( \emph{Pearson's r}= 0.29, \emph{p} \textless{} 0.05).
The difference in target animal fixation proportions between modifier and instrument conditions was higher for participants with better calibration
